---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(indianacovid19data)
```

# indianacovid19data

<!-- badges: start -->
[![R-CMD-check](https://github.com/ercbk/indianacovid19data/workflows/R-CMD-check/badge.svg)](https://github.com/ercbk/indianacovid19data/actions)
<!-- badges: end -->

This R package provides access to most of the processed and raw datasets from [Indiana-COVID-19-Tracker](https://github.com/ercbk/Indiana-COVID-19-Tracker) and [Indiana-COVIDcast-Dashboard](https://github.com/ercbk/Indiana-COVIDcast-Dashboard). Visualizations created using this data can be seen at the [website](https://ercbk.github.io/Indiana-COVID-19-Website/static.html).

## Installation

You can install the latest version of indianacovid19data from Github with:

``` r
# install.packages("remotes")
remotes::install_github("ercbk/indianacovid19data")
```

## File path to .csv format  
indianacovid19data has csv file types for all its datasets in the `inst/extdata` directory.  
```{r}
path_to_file("hosp_msas_line.csv")
```

If the name argument is NULL, then a list of the available files in .csv format is returned
```{r}
path_to_file()
```

